Turbulence in compact to giant H~II regions

### 2023-06-02 strucfunc_paper.tex
Fix typo in equation in section 5.1, penultimate paragraph.
Javier changes for production

%\usepackage{orcidlink}

@@

% Mark new changes in red
\definecolor{NEWcolor}{rgb}{0.7,0.2,0.1}
\newcommand\startNEW{\color{NEWcolor}}
\newcommand\stopNEW{\color{black}}
\newcommand\NEW[1]{\startNEW #1\stopNEW\relax}

@@

% Abstract of the paper
\begin{abstract}
  % Context
  Radial velocity fluctuations on the plane of the sky
  are a powerful tool for studying the turbulent dynamics of emission line regions.
  % What we did
  We conduct a systematic statistical analysis
  of the \halpha{} velocity field for
  a diverse sample of 9 \hii{} regions,
  spanning two orders of magnitude in size and luminosity,
  located in the Milky Way and other Local Group galaxies.
  % How we did it
  By fitting a simple model to the second-order spatial structure function
  of velocity fluctuations, we extract three fundamental parameters:
  the velocity dispersion,
  the correlation length,
  and the power law slope.
  We determine credibility limits for these parameters in each region,
  accounting for observational limitations of noise,
  atmospheric seeing, and the finite map size.
  % What we found
  The plane-of-sky velocity dispersion is found to be a better diagnostic
  of turbulent motions than the line width, especially for lower
  luminosity regions where the turbulence is subsonic.
  The correlation length of velocity fluctuations is found to
  be always roughly 2\% of the \hii{} region diameter,
  implying that turbulence is driven on relatively small scales.
  No evidence is found for any steepening of the structure function
  in the transition from subsonic to supersonic turbulence,
  possibly due to the countervailing effect of projection smoothing.
  Ionized density fluctuations are too large to be explained by the action
  of the turbulence in {\NEW{any}} but the highest luminosity sources.
  A variety of behaviors are seen on scales larger than the correlation length,
  with only a minority of sources showing evidence for homogeneity on the largest scales.
\end{abstract}

@@

\begin{table}
  \begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters are taken from Table 2 of \citet{1984ApJ...287..116K}.
      \NEW{References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.}
      Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The power law slope, \(m\), itself is probably the parameter that
is most sensitive to methodological assumptions.
The fundamental issue is that the observed structure function tends to
show a negative curvature in log-log space at intermediate scales:
\(d\log B/ d\log r < 0\).
This is caused primarily by the steepening due to seeing at small scales
together with the natural asymptotic flattening, 
\(B(r) \to 2 \sigma^2\pos\), at large scales.
As a result, the measured slope depends on the exact range of
separations over which the power law is fitted.
So long as the spatial dynamic range of the observations is high enough,
then a reliable slope can nevertheless be obtained,
as shown by \citet{arthur2016turbulence} for the case of the Orion Nebula.
However, this requires that \(r_0\) should be at least an order of
magnitude higher than the larger of the seeing width
or the minimum separation between spatial points.
This condition is not satisfied for roughly half of our sample regions,
and the same is true for many previous studies.
In such cases, our model-based approach is a more reliable way of
determining the slope.

@@

Based in part on observations obtained at the Kitt Peak National Observatory,
which is operated by the Association of Universities for Research in Astronomy, Inc.,
under cooperative agreement with the National Science Foundation.
Based in part on observations made with the MUSE and FLAMES spectrographs
on VLT telescopes at the La Silla Paranal Observatory, ESO, Chile
under programme IDs 188.B-3002, 076.C-0888 and 098.D-0211.
Based in part on observations made with the William Herschel Telescope
operated by the Isaac Newton Group of Telescopes,
located at the Spanish
\foreignlanguage{spanish}{Roque de los Muchachos}
Observatory of the
\foreignlanguage{spanish}{Instituto de Astrofisica de Canarias}
on the island of La Palma. 
We gratefully acknowledge financial support provided by
\foreignlanguage{spanish}{%
  Dirección General de Asuntos del Personal Académico,
  Universidad Nacional Autónoma de México},
through grant
\foreignlanguage{spanish}{%
  Programa de Apoyo a Proyectos de Investigación
  e Inovación Tecnológica}
IN109823.  
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments
for 30~Doradus derived from MUSE-VLT observations.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.

>>>>

@@

% Mark new changes in red
\definecolor{NEWcolor}{rgb}{0.7,0.2,0.1}
%\newcommand\startNEW{\color{NEWcolor}}
\newcommand\startNEW{\color{black}}
\newcommand\stopNEW{\color{black}}
\newcommand\NEW[1]{\startNEW #1\stopNEW\relax}

@@

% Abstract of the paper
\begin{abstract}
  % Context
  Radial velocity fluctuations on the plane of the sky
  are a powerful tool for studying the turbulent dynamics of emission line regions.
  % What we did
  We conduct a systematic statistical analysis
  of the \halpha{} velocity field for
  a diverse sample of 9 \hii{} regions,
  spanning two orders of magnitude in size and luminosity,
  located in the Milky Way and other Local Group galaxies.
  % How we did it
  By fitting a simple model to the second-order spatial structure function
  of velocity fluctuations, we extract three fundamental parameters:
  the velocity dispersion,
  the correlation length,
  and the power law slope.
  We determine credibility limits for these parameters in each region,
  accounting for observational limitations of noise,
  atmospheric seeing, and the finite map size.
  % What we found
  The plane-of-sky velocity dispersion is found to be a better diagnostic
  of turbulent motions than the line width, especially for lower
  luminosity regions where the turbulence is subsonic.
  The correlation length of velocity fluctuations is found to
  be always roughly 2\% of the \hii{} region diameter,
  implying that turbulence is driven on relatively small scales.
  No evidence is found for any steepening of the structure function
  in the transition from subsonic to supersonic turbulence,
  possibly due to the countervailing effect of projection smoothing.
  Ionized density fluctuations are too large to be explained by the action
  of the turbulence in any but the highest luminosity sources.
  A variety of behaviors are seen on scales larger than the correlation length,
  with only a minority of sources showing evidence for homogeneity on the largest scales.
\end{abstract}

@@

\begin{table}
  \begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters are taken from Table 2 of \citet{1984ApJ...287..116K}.
      References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.
      Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The power law slope, \(m\), itself is probably the parameter that
is most sensitive to methodological assumptions.
The fundamental issue is that the observed structure function tends to
show a negative curvature in log-log space at intermediate scales:
\(d^2 \log B/ d^2 \log r < 0\).
This is caused primarily by the steepening due to seeing at small scales
together with the natural asymptotic flattening, 
\(B(r) \to 2 \sigma^2\pos\), at large scales.
As a result, the measured slope depends on the exact range of
separations over which the power law is fitted.
So long as the spatial dynamic range of the observations is high enough,
then a reliable slope can nevertheless be obtained,
as shown by \citet{arthur2016turbulence} for the case of the Orion Nebula.
However, this requires that \(r_0\) should be at least an order of
magnitude higher than the larger of the seeing width
or the minimum separation between spatial points.
This condition is not satisfied for roughly half of our sample regions,
and the same is true for many previous studies.
In such cases, our model-based approach is a more reliable way of
determining the slope.

@@

Based in part on observations obtained at the Kitt Peak National Observatory,
which is operated by the Association of Universities for Research in Astronomy, Inc.,
under cooperative agreement with the National Science Foundation.
Based in part on observations made with the MUSE and FLAMES spectrographs
on VLT telescopes at the La Silla Paranal Observatory, ESO, Chile
under programme IDs 188.B-3002, 076.C-0888 and 098.D-0211.
Based in part on observations made with the William Herschel Telescope
operated by the Isaac Newton Group of Telescopes,
located at the Spanish
\foreignlanguage{spanish}{Roque de los Muchachos}
Observatory of the
\foreignlanguage{spanish}{Instituto de Astrofisica de Canarias}
on the island of La Palma. 
We gratefully acknowledge financial support provided by
\foreignlanguage{spanish}{%
  Dirección General de Asuntos del Personal Académico,
  Universidad Nacional Autónoma de México},
through grant
\foreignlanguage{spanish}{%
  Programa de Apoyo a Proyectos de Investigación
  e Inovación Tecnológica}
IN109823.  
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments
for 30~Doradus derived from MUSE-VLT observations.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship. 
A sincere thanks to the anonymous referee who help us improve the quality of our work.
